%-------------------------
% Resume in Latex
% Author
% License: MIT
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\setlength{\multicolsep}{0pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\geometry{left=1cm, top=0.5cm, right=1cm,bottom=1cm}

\renewcommand{\labelitemi}{\textbullet}
 % to get bullet points circular 
\setlist[itemize]{label=\textbullet, itemsep=2.5pt, topsep=3pt, parsep=0pt}


\usepackage[most]{tcolorbox}
\tcbset{
  frame code={},
  center title,
  left=0pt,
  right=0pt,
  top=0pt,
  bottom=0pt,
  colback=gray!20,
  colframe=white,
  width=\dimexpr\textwidth\relax,
  enlarge left by=-2mm,
  boxsep=4pt,
  arc=0pt,outer arc=0pt,
}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting

\titleformat{\section}[hang]{\scshape\raggedright\Large}{}{0em}{}[\color{black}\titlerule\vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item{
    \textbf{#1}{\hspace{0.5mm}#2 \vspace{-0.5mm}}
  }
}

\newcommand{\resumePOR}[3]{
  \vspace{0.5mm}\item
  \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1}\hspace{0.3mm}#2 & \textit{\small{#3}}
  \end{tabular*}
  \vspace{-2mm}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{0.5mm}\item
  \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\footnotesize{#4}} \\
    \textit{\footnotesize{#3}} & \footnotesize{#2}\\
  \end{tabular*}
  \vspace{-1.4mm}
}

\newcommand{\resumeProject}[4]{
  \vspace{0.5mm}\item
  \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{\footnotesize{#3}} \\
    \footnotesize{\textit{#2}} & \footnotesize{#4}
  \end{tabular*}
  \vspace{-1.4mm}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\cvsection}[1]{%
  \vspace{4.5mm} % Adjust vertical spacing here
  \begin{tcolorbox}
    \textbf{\large #1}
  \end{tcolorbox}
  \vspace{-6mm}
}


\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%

%---- End of Packages and Functions ------
%-------------------------------------------
%%%%%% CV STARTS HERE %%%%%%%%%%%
%%%%%% DEFINE ELEMENTS HERE %%%%%%%
\newcommand{\name}{Agrim Sangotra} % Your Name
\newcommand{\course}{B.Tech} % Your Program
\newcommand{\branch}{Information Technology} % Your Branch
\newcommand{\phone}{9469199281} % Your Phone Number
\newcommand{\emaila}{agrimsangotra30@gmail.com} % Email 1

\begin{document}
  \fontfamily{cmr}\selectfont

  %----------HEADING-----------------
  \parbox{\dimexpr\linewidth-0.4cm\relax}{
    \begin{tabularx}{\linewidth}{L r}
      \textbf{\Large \name} & {\raisebox{0.0\height}{\footnotesize \faPhone}\ +91-\phone}\\[1.5pt]
      \course, \branch & \href{mailto:\emaila}{\raisebox{0.0\height}{\footnotesize \faEnvelope}\ {\emaila}} \\[1.5pt]
      \href{https://github.com/Agrim-Ani}{\raisebox{0.0\height}{\footnotesize \faGithub}\ {GitHub Profile}} & \href{https://www.linkedin.com/in/agrim-sangotra-203015210}{\raisebox{0.0\height}{\footnotesize \faLinkedin}\ {LinkedIn Profile}}
    \end{tabularx}
  }

  %-----------EDUCATION-----------

\cvsection{Education}
\vspace{10pt}
\resumeSubHeadingListStart
\resumeSubheading
{National Institute of Technology, Srinagar}{CGPA: 7.83}
{B.Tech, Information Technology}{2020 - 2024}
\resumeSubHeadingListEnd


  %-----------Technical skills-----------------
  \cvsection{Technical Skills}
  \vspace{10pt}
  \begin{itemize}[leftmargin=0.05in, label={}, itemsep=2.5pt]
    \small{
      \item \textbf{Languages}{: TypeScript, JavaScript, C++, C\#, PowerShell}
      \item \textbf{Backend \& Web}{: Node.js, Express.js, NestJS, REST APIs, WebSockets, JWT/OAuth 2.0}
      \item \textbf{Cloud \& DevOps}{: Azure (Network Watcher, Load Balancer, VMSS, Managed Identity, Runbooks, Policy, Resource Graph, Service Fabric, HDInsight, AI Foundry), Ev2, Geneva, Docker, Git}
      \item \textbf{Databases}{: MongoDB, PostgreSQL, MySQL, Cosmos DB}
      \item \textbf{Tools \& Practices}{: Postman, Jira, Copilot CLI, CI/CD, Agile}
    }
  \end{itemize}
\vspace{-9pt}
%-----------Experience-----------------
\cvsection{Experience}
\vspace{10pt}
\begin{itemize}[leftmargin=0pt, label={}]
    \item \textbf{Backend Development | HCLTech (Microsoft Client)} \hfill \textit{Sep 2024 -- Present}
  \vspace{1pt}
  \begin{itemize}[leftmargin=*]
    \item Engineered backend services for an SFI resolution platform, with REST APIs integrating a custom Azure AI Foundry model to auto-summarize remediation tasks; automated SFI report-mail generation, cutting vendor reporting time by 90\%.
    \item Built Geneva Kusto-backed APIs powering real-time deployment-health dashboards, cutting manual release verification by 70\%; backend services for release and Ev2 rollout tracking cut report time 90\% and tracking time 50\%.
    \item Owned 13 SFI security workstreams with 100\% on-time resolution, sustaining a $\sim$750 secure score and 4x perfect S360 scores.
    \item Built 11+ Azure Runbook automations cutting manual touch operations by 70\% --- 150+ OS vulnerabilities, 150+ userConfig failures, 300+ untagged Public IPs remediated zero-touch.
    \item Built 8 Ev2 scripts and 8 deployment automation pipeline enabling zero-touch runner infra creation, cutting tagged Public IP usage by 50\%.
    \item Owned dataplane validation infra (MIVnet, Overlake VNet) across 3 Azure clouds, 60+ regions; expanded Managed Identity to 60+ regions for passwordless auth.
    \item Tracked 100\% of service and HDInsight releases at 99\% success, with per-region health insights (SLA delays, exceptions, Service Fabric health) driving failure mitigation.
    \item Executed automated script actions across 50+ HDInsight clusters, 2 clouds, and 17+ prod regions via Ev2 automation to meet customer deadline 50\% faster.
    \item Enabled Azure Load Balancer health probing on VMSS instances; refactored Traffic Analytics auth to tenant-based scoped roles, tightening access governance.
    \item Cut build package size by 10\% via RCA on build localization failures, eliminating recurring pipeline build failures.
  \end{itemize}
  \vspace{8pt}
  \item \textbf{Backend Developer Intern | Mapsense} \hfill \textit{Feb 2024 -- Sep 2024}
  \vspace{1pt}
  \begin{itemize}[leftmargin=*]
      \item Built 80\% of the backend for the Location Intelligence platform end-to-end, sustaining 99\% production uptime.
      \item Implemented OAuth 2.0 Google Sign-In, accelerating registration by 30\%; built profile APIs for invites, uploads, and geo-data workflows.
      \item Built location services (path retrieval, road snapping, session tracking), improving data precision by 40\%; helped secure the first enterprise client (The Nature Conservancy).
  \end{itemize}
\end{itemize}
\vspace{-9pt}


  %-----------Projects-----------------
\cvsection{Personal Projects}
\vspace{12pt}
\begin{itemize}[leftmargin=*, label={}]
  \begin{minipage}[t]{0.48\textwidth}
    \item \textbf{Broadcasting Server: \href{https://broadcasting-server.onrender.com/}{(Link)}}
    \vspace{3pt}
    \begin{itemize}[itemsep=3pt]
      \item \textbf{Description:} Real-time group chat server with shareable room invite links and live presence.
      \item \textbf{Features:} WebSocket messaging, UUID invite links, live presence, message history, JWT auth.
      \item \textbf{Tech:} Node.js, Express.js, WebSocket (ws), MongoDB, Mongoose, JWT.
    \end{itemize}
  \end{minipage}\hfill
  \begin{minipage}[t]{0.48\textwidth}
    \item \textbf{Contact Manager Backend: \href{https://contact-manager-backend-z9l4.onrender.com/api-docs/}{(Link)}}
    \vspace{3pt}
    \begin{itemize}[itemsep=3pt]
      \item \textbf{Description:} Secure REST API for personal contacts; each user accesses only their own data.
      \item \textbf{Features:} JWT-protected routes, registration/login, per-user contact CRUD, MVC architecture.
      \item \textbf{Tech:} Node.js, Express.js, MongoDB, JWT, REST API.
    \end{itemize}
  \end{minipage}
\end{itemize}
\vspace{-13pt}


\end{document}